Speeding up decimal multiplication

### 2020-12-09 paper/paper.tex
Update

For the pre-calculated data, put $\mu = 2^w,$ $p > 2$ is our prime number, and
the value of $p'$ can be calculated with the extended Euclidean algorithm for GCD;
we have $\gcd(p, \mu) = 1,$ so $\exists c_1, c_2 \in \mathbb{Z} \colon c_1 p + c_2 \mu = 1.$
This means $c_1 p \equiv 1 \, (\mymod \, \mu)$ and $-c_1 p \equiv -1 \, (\mymod \, \mu),$ so
$$p' = (-c_1 p) \mymod \mu.$$

>>>>

For the pre-calculated data, put $\mu = 2^w,$ $p > 2$ is our prime number, and
the value of $p'$ can be calculated with the extended Euclidean algorithm for GCD;
we have $\gcd(p, \mu) = 1,$ so $\exists c_1, c_2 \in \mathbb{Z} \colon c_1 p + c_2 \mu = 1.$
This means $c_1 p \equiv 1 \, (\mymod \, \mu)$ and $-c_1 p \equiv -1 \, (\mymod \, \mu),$ so
$$p' = (-c_1) \mymod \mu.$$
